Title here

### 2020-06-23 paper/paper.Rmd
add abstract and some re-arrangement of paragraphs

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- 3 to 6 keywords
- that do not appear in the title
abstract: 
bibliography: biblio.bib
output: rticles::asa_article
editor_options: 
  chunk_output_type: console
---

@@

Given an objective function $f$, one way of optimising it is to equate its gradient to zero. In modern optimisation problems, gradient information can be hard to evaluate or sometimes even impossible and Derivative-Free Optimisation (DFO) methods can be useful to approach these problems. The two most common methods in DFO are *direct-search methods* and *model-based methods* and this paper dedicates to the discussion of direct-search methods, which gains its popularity due to its simplicity in use and reliability in complicated practical problem. Coined by @hooke1961direct, direct search methods don't require any gradient or Hessian information and evaluate $f$ directly. A well-known example of it is the Nelder-Mead algorithm [@nelder1965simplex] and it enjoys the popularity due to its simplicity and reliability. [feel like this sentence can be expanded to include more information. xxx]. Further, direct search methods can be classified as *stochastic* and *deterministic* depends on whether a random sample is used in the search. The stochastic version of  direct-search method is the focus of this paper.

@@

## Projection pursuit guided tour

[doubt if I need the following. xxx]
<!-- A tour path includes two major components: a *generator* that generating the target basis that has higher index value than the current basis and an *interpolator* that performing geodesic interpolation between the current and target basis. An illustration modified from [@buja2005computational] vividly depicts the tour path in guided tour. -->

## problems and difficulties in PP optimisation

@@

The idea of generalising all the diagnostic plots under one framework is inspired by the concept of *grammar of graphic*[@wickham2010layered], which powers the primary graphical system in R, ggplot2 [@ggplot2]. In grammar of graphic, plots are not defined by its appearance (i.e. boxplot, histogram, scatter plot etc) but by "stacked layers". By this design, ggplot doesn't need to develop a gazillion of functions that each produces a different type of plot. Instead, it creates aesthetic mapping from the variables to the geometric objects and builds the plot through different layers.

[Do I need this paragraph to details the grammar of graphic? xxx]
<!-- A layer includes 1) the data that powers the plot; 2) a geometric object that represents the visual shape of the data and 3) relevant statistical transformation that transform the information in the data to the information used to draw the geometric object. An important concept in the grammar of graphic is *aesthetic mapping*. Aesthetic mapping links the variable in a dataset to information needed to produce a geometric object. For example, we map one variable on the x-axis and another on the y-axis to create a scatterplot. Another example of creating a boxplot involves 1) mapping one variable on the x-axis and 2) transforming another variable to its five-point-summary and mapping the five-point-summary to the y-axis.  -->

@@

>>>>

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- optimisation
- projection pursuit 
- guided tourr
- visual 
- diagnostics 
- R
abstract: Friedman & Tukey commented on their intial paper on projection pursuit in 1974 that "the  technique  use  for  maximising  the  projection index strongly influences both the statistical and the computational aspects of the procedure." While many projection pursuit indices have been proposed in the literature, few concerns the optimisation procedure. In this paper, we developed a system of diagnostics aiming to visually learn how the optimisation procedures find its way towards the optimum. This diagnostic system can be applied to more general to help practitioner to unveil the black-box in randomised iteartive (optimisation) algorithms. An R package, ferrn, has been created to implement this diagnostic system.
bibliography: biblio.bib
output: rticles::asa_article
editor_options: 
  chunk_output_type: console
---

@@

Given an objective function $f$, one way of optimising it is to equate its gradient to zero. In modern optimisation problems, gradient information can be hard to evaluate or sometimes even impossible and Derivative-Free Optimisation (DFO) methods can be useful to approach these problems. One common class of methods in DFO is *Direcct-search methods*. Coined by @hooke1961direct, direct search methods don't require any gradient or Hessian information and has gained its popularity through its simplicity in use and reliability in solving complicated practical problems. Depends on whether a random sample is used in the search, this class of methods can be further classified as *stochastic* or *deterministic*.  The stochastic version of the direct-search methods will be the main optimisation procedure analysed in this paper.

@@

<!-- The two most common methods in DFO are *direct-search methods* and *model-based methods* and this paper dedicates to the discussion of direct-search methods, which .  -->

<!-- A well-known example of it is the Nelder-Mead algorithm [@nelder1965simplex] and it enjoys the popularity due to its simplicity and reliability. [feel like this sentence can be expanded to include more information. xxx]. -->

section 1: DFO

section 2: idea of diagnostic system & global object

section 3: general intro to tourr

section 4: apply diagnostic system + simulated data

section 5: plots

## Motivation to visaul diagnostics

@@

The idea of generalising all the diagnostic plots under one framework is inspired by the concept of *grammar of graphic*[@wickham2010layered], which powers the primary graphical system in R, ggplot2 [@ggplot2]. In grammar of graphic, plots are not defined by its appearance (i.e. boxplot, histogram, scatter plot etc) but by "stacked layers". By this design, ggplot doesn't need to develop a gazillion of functions that each produces a different type of plot. Instead, it aesthetically maps the variables to the geometric objects and builds the plot through different layers.

<!-- [Do I need this paragraph to details the grammar of graphic? xxx - don't think so; not particularly relevant - assume most people know it roughly] -->
<!-- A layer includes 1) the data that powers the plot; 2) a geometric object that represents the visual shape of the data and 3) relevant statistical transformation that transform the information in the data to the information used to draw the geometric object. An important concept in the grammar of graphic is *aesthetic mapping*. Aesthetic mapping links the variable in a dataset to information needed to produce a geometric object. For example, we map one variable on the x-axis and another on the y-axis to create a scatterplot. Another example of creating a boxplot involves 1) mapping one variable on the x-axis and 2) transforming another variable to its five-point-summary and mapping the five-point-summary to the y-axis.  -->

@@

# Projection pursuit guided tour

[doubt if I need the following. xxx - maybe an algorithmatic version of guide tour would be helpful for non-expert to understand the method?]
<!-- A tour path includes two major components: a *generator* that generating the target basis that has higher index value than the current basis and an *interpolator* that performing geodesic interpolation between the current and target basis. An illustration modified from [@buja2005computational] vividly depicts the tour path in guided tour. -->

# Visual diagnostic in guided tour
